Notes on Wide Gap

### 2016-04-23 paper/wide_gap_notes.tex

>>>>

\section{Base Flow}
In a viscous, Taylor-Couette device, there is only one base state that
satisfies no-slip boundary conditions and the Navier-Stokes
equations. This is called Couette flow, and can be written as
\begin{equation}
  \label{eq:couette_flow}
  \Omega(r) = a + \frac{b}{r^2},
\end{equation}
where $a = (\Omega_2 r^2_2 - \Omega_1 r^2_1)/(r^2_2 - r^2_1)$ and
$b = r^2_1 r^2_2 (\Omega_1 - \Omega_2)/(r^2_2 - r^2_1)$. Here,
$\Omega_1$ is the rotation rate at the inner cylinder radius $r_1$,
and likewise for the outer cylinder $r_2$.

Keplerian flow is $\Omega \propto r^{-3/2}$; these appear to be
incompatible. However, in Couette flow, we can approximate Keplerian
flow by creating what is called ``quasi-Keplerian'' flow.

Defining $q \equiv -d \ln \Omega/d \ln r$, we can see that for Couette flow,
\begin{equation}
  \label{eq:couette_q}
  q \equiv -\frac{d \ln \Omega}{d \ln r} = \frac{2 b}{a r^2 + b}.
\end{equation}
Thus, assuming $r_1$ and $r_2$ are fixed by the experiment, through
judicious choices of $\Omega_1$ and $\Omega_2$, we can make
$q(r_0) = 3/2$, where $r_0$ is some reference radius. Goodman \& Ji do
exactly this with $\bar{\zeta}$.

So, we have to choose $\Omega(r) = a + b/r^2$; everywhere it appears in our equations.
